An Ethnography of Online Performance Artists

### 2017-03-17 proposals/Brown_Magic_Grant_2017/main.tex
abstract changes (hah, get it?)

\lhead{} % controls the left corner of the header
% \chead{} % controls the center of the header
\rhead{Alkhatib \& Nagy} % controls the right corner of the header
\lfoot{last updated} % controls the left corner of the footer
\cfoot{} % controls the center of the footer
\rfoot{Page~\thepage} % controls the right corner of the footer
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}

@@

% \setlength{\parskip}{.2em}

@@

\def\maketitle{%
\par{\centering {\scshape \LARGE \textbf{\@title}}%
\par{\@author}
\par{DRAFT \DTMcurrenttime~\today}%
% \par{DRAFT \DTMcurrenttime~on~\today}%
\par}}
% \smallskip \hrule \smallskip }

@@

\begin{document}
  \maketitle
  \begin{abstract}
  \ali{something along the lines of: online performers are becoming a big deal, and
       these performers are possibly the forerunners of a new type of expression and art.
       The frustration and turmoil they're experiencing
       --- both interpersonally and with the environment on which they ``work'' ---
       demands to be better understood if we hope to make informed design decisions that empower these people.
       We propose to conduct ethnographic fieldwork of this domain,
       initially informed by a historical framing, but
       ultimately studying how digitally mediated publics such as these affect
       the politics of this group of performers.}
  \end{abstract}

@@

% \section*{Insight}
\topic{We recognize that \textit{historical analysis}
% Studying contemporary phenomena through an established framing
can be a helpful way of
making sense of contemporary phenomena.}
As we found in a recent paper framing crowd work and gig work as a modern instantiation of \textit{piecework},
scholarship from a parallel or similar domain can
provide us some grounding to make sense of what we've seen, as well as inform predictions~\cite{pieceworkCrowdworkGigwork}.

>>>>

\lhead{} % controls the left corner of the header
% \chead{} % controls the center of the header
\rhead{Ali Alkhatib \& Jeff Nagy} % controls the right corner of the header
\lfoot{} % controls the left corner of the footer
\lfoot{last updated \DTMcurrenttime~\today} % controls the left corner of the footer
\cfoot{} % controls the center of the footer
\rfoot{} % controls the right corner of the footer
% \rfoot{Page~\thepage} % controls the right corner of the footer
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}

@@

@@

\def\maketitle{%
\par{\centering {\scshape \LARGE \textbf{\@title}}%
\par{\@author}
\par{DRAFT \DTMcurrenttime~\today}%
\par}}
% \smallskip \hrule \smallskip }

@@

\begin{document}
  \maketitle
  \begin{abstract}
  Online video sharing and streaming platforms have grown quickly in the past decade
  to support an emerging community of unconventional entertainers.
  This eclectic group of artists has collectively been
  exploring boundaries and experimenting with styles and expectations,
  critically influencing both our cultural expectations of performers and the norms of performance itself.
  But these dramatic shifts have coincided with turmoil among this new class of entertainers and artists.
  The frustration and turmoil they're experiencing
  --- both with one another and with the very platform on which they ``work'' ---
  calls for a better understanding of the culture and position of this nascent culture.
  We propose to conduct ethnographic fieldwork in this domain,
  initially informed by a historical framing, but
  ultimately studying how digitally mediated publics such as these affect
  the politics of this group of performers.
  \end{abstract}

@@

% \section*{Insight}
\topic{\textit{Historical analysis}
% Studying contemporary phenomena through an established framing
can be a helpful way of
making sense of contemporary phenomena and informing early fieldwork.}
As we found in a recent paper framing crowd work and gig work as a modern instantiation of \textit{piecework},
scholarship from a parallel or similar domain can
provide us some grounding to make sense of what we've seen and offer a framework for making reasonable predictions~\cite{pieceworkCrowdworkGigwork}.
We believe that a similar approach can be used here to help make sense of online streaming and video performances.
